# Assignments and Grading
This section provides general details on the different types of assignments for this course. It also contains policies for submitting work, receiving feedback, and late work. A summary schedule with all due dates is available as part of the [Course Schedule](course-schedule.html).

```{r, echo=FALSE}
schedule_assign_tbl <- readr::read_csv("schedule_assignments.csv", 
                                col_types = readr::cols(
                                  assignment = readr::col_character(),
                                  date = readr::col_character()
  ))

schedule_assign_tbl <- dplyr::filter(schedule_assign_tbl, is.na(assignment) == FALSE)

schedule_assign_tbl <- dplyr::mutate(schedule_assign_tbl, date = lubridate::mdy(date))
schedule_assign_tbl <- dplyr::mutate(schedule_assign_tbl, month = lubridate::month(date))
schedule_assign_tbl <- dplyr::mutate(schedule_assign_tbl, month = month.name[month])
schedule_assign_tbl <- dplyr::mutate(schedule_assign_tbl, day = lubridate::day(date))
schedule_assign_tbl <- dplyr::mutate(schedule_assign_tbl, dow = weekdays(date, abbreviate = FALSE))
schedule_assign_tbl <- dplyr::mutate(schedule_assign_tbl, label = paste0(dow, ", ", month, " ", day))
```

## Assignments
Your grade for this course will consist of a number of different assignments on which points may be earned. Each category of assignment is described below.

### Attendance and Participation

```{block, type = "rmdtip"}
Attendance and participation are worth 50 points, or **10%** of your final grade.
```

As discussed above, both attendance and participation are important aspects of this class. The class participation grade will be based on (a) attendance, (b) level of engagement during lectures and labs, (c) level of engagement on Canvas, and (d) the completion of other exercises including "entry" and "exit" tickets, the student information sheet, a pre-test, and an end of the semester course evaluation. 

Each of these elements is assigned a point value and assessed using a scale that awards full, partial, or no credit (see [Grading](grading.html)). Not attending class or completing an "entry" or "exit" ticket will result in no credit being earned for that element on a given day. Disengagement during class may result in partial or no credit being earned. Late arrivals will result in only partial credit earned for that element on a given day.

Your participation grade will be split, with 25 points each for Part 1 (through Spring Break) and Part 2 (from Spring Break onward). Since the number of points awarded for participation are variable, the total number of points earned for each half will be **weighted** so that it is converted to a final score that matches the points available for that part of the course. I provide the final number of points earned for each part of the course. If you would like a more detailed breakdown of your participation grade and/or attendance record, please reach out and I will happily provide one.

### Lab Exercises

```{block, type = "rmdtip"}
Labs are worth 140 points, or **28%** of your final grade.
```

Each course meeting will include time dedicated to practicing the techniques and applying the theories described in the meeting's materials. These exercises will give you an opportunity to practice skills that correspond with the first four course objectives. Instructions for the labs will be posted in the lecture repositories on [**GitHub**](https://github.com/slu-soc5650) and will be linked to from the lecture pages on the [**course website**](https://slu-soc5650.github.io/). The instructions will also detail the deliverables to be submitted to demonstrate completion of each assignment. Replication files are also provided in the lecture repositories on [**GitHub**](https://github.com/slu-soc5650).

There will be a total of fourteen lab exercises over the course of the semester, each of which is worth 2% of your final grade. Lab exercises are graded using the "check" grading system. Since replication files are posted, feedback for labs is not generally returned after the first few assignments and I will only respond with the number of points awarded if you do not earn full credit. *It is your responsibility to reach out to discuss questions or concerns you had while doing the lab.*

### Final Project

```{block, type = "rmdtip"}
The final project is worth 310 points, or **62%** of your final grade. The waypoints are worth **24%** of your final grade, and the final deliverables are worth **38%** of your final grade. Deliverables vary by section; see below for details.
```

The final project corresponds with the fourth learning outcome. It will be organized slightly differently depending on which section you are enrolled in. Specific instructions will be provided in the [**final project guide**](https://slu-soc5650.github.io/final-project). 

As work progresses, there will be a number of **waypoints** where students will need to submit updates on their progress. Waypoints serve as the homework assignments for this class - this is your opportunity to show me how your skills are developing *and* make progress on your final project. They are generally due two weeks after the relevant topic is first introduced in class. The six waypoints are as follows:

  1. `r schedule_assign_tbl$assignment[2]` - **`r schedule_assign_tbl$label[2]`** - memo submission
  2. `r schedule_assign_tbl$assignment[3]` - **`r schedule_assign_tbl$label[3]`** - initial data cleaning
  3. `r schedule_assign_tbl$assignment[4]` - **`r schedule_assign_tbl$label[4]`** - combining data sources
  4. `r schedule_assign_tbl$assignment[5]` - **`r schedule_assign_tbl$label[5]`** - projecting data
  5. `r schedule_assign_tbl$assignment[6]` - **`r schedule_assign_tbl$label[6]`** - geoprocessing data
  6. `r schedule_assign_tbl$assignment[7]` - **`r schedule_assign_tbl$label[7]`** - draft story map

Deliverables for each waypoint are described in the [**final project guide**](https://slu-soc5650.github.io/final-project). All waypoints are graded using the "check" grading system. Final materials will be due on **`r schedule_assign_tbl$label[11]`** (during Finals Week). Final deliverables differ by course section.

#### SOC 4650
If you are enrolled in SOC 4650, you will need to create a story map that features some introductory information, media, and thematic maps about your topic.

```{r, echo=FALSE}
final4015 <- data.frame(
  Assignment = c("Waypoints", "Final Code & Docs", "Final Storymap"),
  Points = c("20 pts", "80 pts", "110 pts"),
  Quantity = c("x6", "x1", "x1"),
  Total = c("120 pts", "80 pts", "110 pts"),
  stringsAsFactors = FALSE
)

knitr::kable(
  final4015, booktabs = TRUE,
  caption = "SOC 4650 Final Project Breakdown"
)
```

#### SOC 5650
If you are enrolled in SOC 5650, you will need to create a story map that features some introductory information, media, and thematic maps about your topic. In addition, you will need to write a 3000-4000 word final paper written in the style of an empirical journal article. The following additional deadlines apply:

1. `r schedule_assign_tbl$assignment[8]` - **`r schedule_assign_tbl$label[8]`** - annotated Bibliography with a minimum of fifteen peer reviewed sources
2. `r schedule_assign_tbl$assignment[9]` - **`r schedule_assign_tbl$label[9]`** - draft paper due
3. `r schedule_assign_tbl$assignment[10]` - **`r schedule_assign_tbl$label[10]`** - peer reviews of the draft paper and analysis development due as a GitHub issue in partner's final project repository (graded as part of your draft paper grade)
4. The final paper is due **`r schedule_assign_tbl$label[11]`** along with the rest of the final project.

Grading for SOC 5650 is broken down as follows:

```{r, echo=FALSE}
final4015 <- data.frame(
  Assignment = c("Waypoints", "Annotated Bibliography", "Draft Paper", "Final Code & Docs", "Final Storymap", "Final Paper"),
  Points = c("20 pts", "20 pts", "20 pts", "40 pts", "55 pts", "55 pts"),
  Quantity = c("x6", "x1", "x1", "x1", "x1", "x1"),
  Total = c("120 pts", "20 pts", "20 pts", "40 pts", "55 pts", "55 pts"),
  stringsAsFactors = FALSE
)

knitr::kable(
  final4015, booktabs = TRUE,
  caption = "SOC 5650 Final Project Breakdown"
)
```

## Submission and Late Work

### Assignment Submission

Copies of all assignment requested deliverables should be uploaded to your private assignments repository on [GitHub](https://github.com/slu-soc5650) before class on the day that the assignments are due. All assignments will contain details on required deliverables.

The GitHub submission policy is in place because it facilitates clear, easy grading that can be turned around to you quickly. Submitting assignments in ways that deviate from this policy will result in a late grade (see below) being applied in the first instance and a zero grade for each subsequent instance.

### Licensing of Student Work

All assignment repositories are licensed under a [Creative Commons Attribution-NonCommercial-NoDerivatives 4.0 International License](https://creativecommons.org/licenses/by-nc-nd/4.0/). This license explicitly gives you copyright to all work you create for this course. The license gives Chris permission to copy your work (such as for grading) and to re-use your work later for non-commercial purposes (such as in-class examples) so long as you are given credit for it. However, your work cannot be used for monetary gain (such as in a textbook) and derivative works based on your work are prohibited.

The syllabus agreement at the end of the Student Information Sheet includes an acknowledgment of this licensing arrangement. If you have questions about this, please contact Chris before submitting the form.

### Late Work

Once the class begins, any assignments submitted will be treated as late. Assignments handed in within 24-hours of the beginning of class will have 15% deducted from the grade. I will deduct 15% per day for the next two 24-hour periods that assignments are late. After 72 hours, I accept late work at half credit. It is imperative that you avoid missing assignments. They build upon each other, and students can easily find themselves weeks behind on coursework in this class.

If you cannot attend class because of personal illness, a family issue, jury duty, an athletic match, or a religious observance, you must contact me beforehand to discuss alternate submission of work.

## Extra Credit

From time to time I may offer extra credit to be applied to your final grade. I will only offer extra credit if it is open to the entire class (typically for something like attending a lecture or event on-campus). If I offer extra credit, I will typically require you to submit a short written summary of the activity within a week of the event to obtain the credit. When offered, extra credit opportunities cannot be made-up or substituted if you are unable to attend the event.

## Grading

Grades will be included with assignment feedback, which will be disseminated through Github’s **Issues** tool. At midterms, Lecture-17, and finals, I will upload a summary of all assignment grades to a new **Issue** on GitHub.

All grades that use a “check” system (the lecture preps, labs, and some aspects of the final project) will be calculated using the following approach. A “check-plus” represents excellent work and will get full credit. A “check” represents satisfactory work and will get 85% of the points available for that assignment. A “check-minus” represents work that needs substantial improvement and will get 75% of the points available for that assignment.

I use a point system for calculating grades. The following table gives the weighting and final point totals for all assignments for this course:

```{r, echo=FALSE}
points <- data.frame(
  Assignment = c("Participation", "Labs", "Final Project"),
  Points = c("25 pts", "10 pts", "310 pts"),
  Quantity = c("x2", "x14", "x1"),
  Total = c("50 pts", "140 pts", "310 pts"),
  Percent = c("10%", "28%", "62%"),
  stringsAsFactors = FALSE
)

knitr::kable(
  points, booktabs = TRUE,
  caption = "SOC 4650 and 5650 Points Breakdown"
)
```

All feedback will include grades that represent number of points earned. If you want to know your percentage on a particular assignment, divide the number of points earned by the number of points possible and then multiply it by 100.

Final grades will be calculated by taking the sum of all points earned and dividing it by the total number of points possible (1,000). This will be multiplied by 100 and then converted to a letter grade using the
following table:

```{r, echo=FALSE}
grades1 <- data.frame(
  GPA = c("4.0", "3.7", "3.3", "3.0", "2.7"),
  Letter = c("A", "A-", "B+", "B", "B-"),
  Percent = c("93.0% - 100%", "90.0% - 92.9%", "87.0% - 89.9%", "83.0% - 86.9%", "80.0% - 82.9%"),
  stringsAsFactors = FALSE
)

grades2 <- data.frame(
  GPA = c("2.3", "2.0", "1.7", "1.0", "0.0"),
  Letter = c("C+", "C", "C-", "D", "F"),
  Percent = c("77.0% - 79.9%", "73.0% - 76.9%", "70.0% - 72.9%", "63.0% - 69.9%", "< 63.0%"),
  stringsAsFactors = FALSE
)

knitr::kable(
  list(
    grades1,
    grades2
  ),
  caption = "Course Grading Scale", booktabs = TRUE
)
```

Borderline grades (i.e. a grade within half a percentage point of the next highest letter grade) *will* be rounded up before final grade submission at the end of the semester. A grade of 89.6% would therefore be submitted to SLU as an "A-" while a grade of 89.4% would be submitted to SLU as a "B+". The final grade report will include both the original letter grade and the rounded letter grade if applicable.

```{block, type = "rmdwarning"}
No chances will be given for revisions of poor grades. Incomplete grades will be given upon request only if you have a "C" average and have completed at least two-thirds of the assignments. You should note that incomplete grades must be rectified by the specified deadline or they convert to an "F".
```
