# (PART) Reading List {-}

```{r, echo=FALSE, message=FALSE}
schedule_tbl <- readr::read_csv("schedule.csv", 
                                col_types = readr::cols(
                                  module = readr::col_character(),
                                  date = readr::col_character(),
                                  start = readr::col_logical()
  ))
schedule_tbl <- dplyr::mutate(schedule_tbl, date = lubridate::mdy(date))
schedule_tbl <- dplyr::mutate(schedule_tbl, month = lubridate::month(date))
schedule_tbl <- dplyr::mutate(schedule_tbl, month = month.name[month])
schedule_tbl <- dplyr::mutate(schedule_tbl, day = lubridate::day(date))
schedule_tbl <- dplyr::mutate(schedule_tbl, dow = weekdays(date, abbreviate = FALSE))
schedule_tbl <- dplyr::mutate(schedule_tbl, label = paste0(dow, ", ", month, " ", day))
```

# Course Schedule

The following is a high-level schedule that details the general topic covered by each lecture.

```{r, echo=FALSE}
schedule <- data.frame(
  Module = c("**1**", "", "", "", "**2**", "", "",
             "**3**", "", "", "", "**4**", "", "", "",
             "", ""),
  Meeting = c("", "1-1", "1-2", "1-3", "", "2-1", "2-2",
              "", "3-1", "3-2", "3-3", "", "4-1", "4-2", "4-3",
              "4-4", "4-5"),
  Date = c("", 
           schedule_tbl$label[1],
           schedule_tbl$label[2],
           schedule_tbl$label[3],
           "",
           schedule_tbl$label[4],
           schedule_tbl$label[5],
           "",
           schedule_tbl$label[6],
           schedule_tbl$label[7],
           schedule_tbl$label[8],
           "",
           schedule_tbl$label[9],
           schedule_tbl$label[10],
           schedule_tbl$label[11],
           schedule_tbl$label[12],
           schedule_tbl$label[13]
           ),
  Title = c("**Getting Started**",
            "Course Introduction",
            "Map Production Basics",
            "Cartography 101",
            "**Data Cleaning**",
            "Data Cleaning Basics",
            "Combining Data Sources",
            "**Geoprocessing**",
            "Working with Map Projections",
            "Intersect, Select, and Aggregate",
            "Union, Dissolve, and Merge",
            "**Map Products**",
            "ArcGIS Online",
            "Story Maps, Part 1",
            "Story Maps, Part 2",
            "Print Maps, Part 1",
            "Print Maps, Part 2"
            ),
  stringsAsFactors = FALSE
)

knitr::kable(
  schedule, booktabs = TRUE,
  caption = "SOC 4650/5650 Course Overview"
)
```

### Scheduling Notes

The course schedule may change as it depends on the progress of the class and the challenges we are confronted by this semester. The web version of this document will be updated to reflect any alterations, but the `.pdf` version will remain unaltered.

This semester, we will not have class on **March 15th** and **April 18th**  because they fall on University breaks. Additionally, no class activities are scheduled for **May 9th**. This is a **"flex day,"** which I have left without a scheduled plan to accommodate changes due to COVID-19. If we have to reschedule class days, this date will be used before we begin to remove content from the course plan. I will provide updates on my plans for this day as the semester progresses.

Additionally, evening classes are often held on the Monday after Easter, which falls on **April 18th** this year. If we have already used the flex day, I may elect to hold class that evening.
